---
title: "Lab 01 - Hello R"
author: "Allison Li"
date: "20250121"
output: 
  html_document: 
    fig_width: 6
    fig_height: 7
---

## Load packages and data

```{r load-packages, message=FALSE}
install.packages("tidyverse")
install.packages("datasauRus")
library(tidyverse) 
library(datasauRus)
```

## Exercises

### Exercise 1

There are 1846 rows and 3 variables. The variables are dataset, x, and y. 

### Exercise 2

```{r plot-dino, fig.height=4, fig.width=5}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")

ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```
This nonlinear relationship has indicated a slightly negative correlation between the variables x and y, as r= -.064. Having a visualized graph of the correlation helps us better understand the graph in terms of whether it is a curve or linear. 

### Exercise 3

```{r plot-star, fig.height=4, fig.width=5}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")

ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

The correlation between x and y in the dataset:

```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))
```
Add your explanation here—what did you notice?
the correlation for the star dataset is -.063. Although the r value is almost the same as the r value for the dino dataset, as we can see the graph is very different. This indicates that visualizing the relationships for the data is very important.  

### Exercise 4

Add your code and narrative to complete this exercise. Use the conventions from the previous exercises to name your chunks and organize your work.

```{r plot-circle, fig.height=5, fig.width=5}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")

ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

the correlation between x and y for the circle dataset:
```{r cor-circle}
circle_data %>%
  summarize(r = cor(x, y))
```
the r value for the circle dataset is -.068, which is slightly more negative than the r value for the dino dataset. However, the r value still has limited indication for the relationship since the dataset is not a simple linear correlation. 

### Exercise 5

This is your final exercise! Add code and narrative as needed. Be creative and show off what you’ve learned so far.
Add code and narrative as needed.

To add additional R chunks, you can either type the backticks, curly braces, and the letter `r`, or use the "Insert Chunk" button above (the green C+ icon). Have fun!

```{r}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset)) +
  geom_point() +
  facet_wrap(~dataset, ncol = 3) +
  theme(legend.position = "none")

datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```



